Modeling Time-Variable Elemental Abundances in Coronal Loop Simulations

### 2024-06-08 src/tex/ms.tex
[showyourwork] overleaf sync

\section*{Acknowledgments}
All of the tools used to produce this paper are open-source.  At the time of writing, the implementation into \texttt{ebtel++} is publicly available as an unmerged pull request on GitHub: \url{https://github.com/rice-solar-physics/ebtelPlusPlus/pull/87}.

This paper is fully reproducible with the \href{https://github.com/showyourwork/showyourwork}{\showyourwork} package, and can be downloaded from \url{https://github.com/jwreep/ebtel_abundances}.  This package strives for full reproducibility and transparency in science.  Each figure in this paper contains a hyperlink with the Github logo that points to the script used to generate the plots in that figure.  Additionally, the whole paper can be generated with a single command (`showyourwork build`) that will run the \texttt{ebtel++} simulations, read in the data, and produce the figures.  Users can then additionally reconfigure the simulations, the plots, or the scripts to their own liking to validate or extend this research.

>>>>

\section*{Acknowledgments}
\textbf{All of the tools used to produce this paper are open-source.}  At the time of writing, the implementation into \texttt{ebtel++} is publicly available as an unmerged pull request on GitHub: \url{https://github.com/rice-solar-physics/ebtelPlusPlus/pull/87}.

This paper is fully reproducible with the \href{https://github.com/showyourwork/showyourwork}{\showyourwork} package, and can be downloaded from \url{https://github.com/jwreep/ebtel_abundances}.  \textbf{This package strives for full reproducibility and transparency in science.  Each figure in this paper contains a hyperlink with the Github logo that points to the script used to generate the plots in that figure.  Additionally, the whole paper can be generated with a single command (`showyourwork build`) that will run the \texttt{ebtel++} simulations, read in the data, and produce the figures.  Users can then additionally reconfigure the simulations, the plots, or the scripts to their own liking to validate or extend this research.}
